New lower bounds for Schur and weak Schur numbers

### 2021-10-13 article/weakschur.tex
plus de exist + pdf 13/10

Let \((p, k), (q, n) \in (\mathbb{N}^*)^2\) such that there exists a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets. Let \(a \in \mathbb{N}\) with \(a > q\)
and let us try to build a coloring of \([\![1, ap + q]\!]\) into \(n + k\) weakly sum-free subsets. Let
\(l = a - q - 1\), \(r \in [\![1,q]\!]\) and \(w = a - l - r - 1 = q - r\).

@@

\begin{definition}
Let \( (n,b) \in (\mathbb{N}^*)^2\). If there exists \(a\) such that there exists a \(b\)-WS-template with width \(a\)
and \(n\) colors, we define :
\[
\WS_b^+(n)= \max \{a \in \mathbb{N}^*/ \text{there exists a } b \text{-WS-template with width } a \text{ and } n \text{ colors} \}.
\]
If no such \(a\) exists, we set \(\WS_b^+(n) = 0\).
\end{definition}

@@

\begin{proof}[\textsc{Proof of Theorem \ref{thm:WS-ab}.}]
\label{PreuveThm}
Let \((q, n) \in (\mathbb{N}^*)^2\) such that there exists a partition of \([\![1, q]\!]\) into n weakly sum-free subsets. 
Let \(f: [\![1, q]\!] \rightarrow [\!]1, n]\!]\) a weakly sum-free colouring.
Let \(b=q\) and \(a = q + \left \lceil \dfrac{q}{2} \right \rceil + 1\). A new colouring \(g\) is defined as follows:

@@

\begin{proposition}
\label{prop:tunelastrow}
Let \((b, k, a) \in (\mathbb{N}^*)^3\) and let \(f\) be a coloring associated to a \(b\)-WS-template with width \(p\) and \(k\) colors. Let
\(c \in \mathbb{N}\) and assume there there exists a coloring \(g\) of \([\![b + 1, b + c]\!]\) with \(k\) colors such that for all \(c \in [\![1, k]\!]\),

@@

\begin{theorem}
\label{thm:compWStemp}
Let \((k,p) \in (\mathbb{N}^*)^2\) and \((a, n, b) \in (\mathbb{N}^*)^3\). If there exists a S-template with width
\(p\) and \(k+1\) colors and a \(b\)-WS-template with width \(a\) and \(n\) colors, then there exists a \(pb\)-WS-template
with width \(pq\) and \((n+k)\) colors.
\end{theorem}

>>>>

Let \((p, k), (q, n) \in (\mathbb{N}^*)^2\) such that there are a partition of \([\![1,q]\!]\) into \(n\) weakly sum-free
subsets and a partition of \([\![1,p]\!]\) into \(k\) sum-free subsets. Let \(a \in \mathbb{N}\) with \(a > q\)
and let us try to build a coloring of \([\![1, ap + q]\!]\) into \(n + k\) weakly sum-free subsets. Let
\(l = a - q - 1\), \(r \in [\![1,q]\!]\) and \(w = a - l - r - 1 = q - r\).

@@

\begin{definition}
Let \( (n,b) \in (\mathbb{N}^*)^2\). If there is \(a\) such that there is a \(b\)-WS-template with width \(a\)
and \(n\) colors, we define :
\[
\WS_b^+(n)= \max \{a \in \mathbb{N}^*/ \text{there is a } b \text{-WS-template with width } a \text{ and } n \text{ colors} \}.
\]
If there is no such \(a\), we set \(\WS_b^+(n) = 0\).
\end{definition}

@@

\begin{proof}[\textsc{Proof of Theorem \ref{thm:WS-ab}.}]
\label{PreuveThm}
Let \((q, n) \in (\mathbb{N}^*)^2\) such that there is a partition of \([\![1, q]\!]\) into n weakly sum-free subsets. 
Let \(f: [\![1, q]\!] \rightarrow [\!]1, n]\!]\) a weakly sum-free colouring.
Let \(b=q\) and \(a = q + \left \lceil \dfrac{q}{2} \right \rceil + 1\). A new colouring \(g\) is defined as follows:

@@

\begin{proposition}
\label{prop:tunelastrow}
Let \((b, k, a) \in (\mathbb{N}^*)^3\) and let \(f\) be a coloring associated to a \(b\)-WS-template with width \(p\) and \(k\) colors. Let
\(c \in \mathbb{N}\) and assume there is a coloring \(g\) of \([\![b + 1, b + c]\!]\) with \(k\) colors such that for all \(c \in [\![1, k]\!]\),

@@

\begin{theorem}
\label{thm:compWStemp}
Let \((k,p) \in (\mathbb{N}^*)^2\) and \((a, n, b) \in (\mathbb{N}^*)^3\). If there are a S-template with width
\(p\) and \(k+1\) colors and a \(b\)-WS-template with width \(a\) and \(n\) colors, then there is a \(pb\)-WS-template
with width \(pq\) and \((n+k)\) colors.
\end{theorem}
